Supplemental Materials, Methods and Results

### 2021-04-22 ms.Rmd
Adding code now. Figure for social context done

```{r getlibrary, echo = FALSE, results = "hide"}
# load libraries
devtools::install_github("karthik/wesanderson")
pacman::p_load(lme4, lmerTest, ggplot2, lsmeans, emmeans, multcomp, dplyr, wesanderson, patchwork, latex2exp)

@@

@@

# Display dl
    ConspicDisplayAC <- lmer(dL ~ SVL + Population + (1|ID), data=Display_1)
    summary(ConspicDisplayAC)
    anovaConspicDisplayAC <- anova(ConspicDisplayAC)

## Display dS
         ConspicDisplayCC <- lmer(dS ~ SVL + Population + (1|ID), data=Display_1)
    anovaConspicDisplayCC <- anova(ConspicDisplayCC)

@@

Courtship <- read.table("./data/Courtship_1.2.csv", 
                          header=TRUE, sep=",", dec=".", strip.white=TRUE)

# Courtship dl
ConspicCourtshipAC <- lmer(dL ~ SVL + Population  + (1|ID), data=Courtship)
courship_anovaAC <- anova(ConspicCourtshipAC)

# Courtship dS
  ConspicCourtshipCC <- lmer(dS ~ SVL + Population  + (1|ID), data=Courtship)
courship_anovaCC <- anova(ConspicCourtshipCC)
```

@@

We conducted experiments manipulating both the social and predatory context chameleons encountered, in both their native Kenyan range and their introduced Hawaiian range, to test three hypotheses about colour signal evolution. First, we tested the hypothesis that relaxed predation pressure results in character release of a dynamic visual signal. Sexual selection favours more conspicious signals and these should evolve to be more conspicuous without predators. In suppor of this prediction, male display colouration exhibited in social contexts (i.e., male-male contests and courtship) was more conspicuous to a conspecific in Hawaii compared with Kenya (**Male-Male Contests**: Acromatic ($dl$); $F_{`r anovaConspicDisplayAC$NumDF[2]`,`r anovaConspicDisplayAC$DenDF[2]`}$ = `r anovaConspicDisplayAC[5][2,]`, p = `r p_value(anovaConspicDisplayAC[6][2,])`; Chromatic ($dS$): $F_{`r anovaConspicDisplayCC$NumDF[2]`,`r anovaConspicDisplayCC$DenDF[2]`}$ = `r anovaConspicDisplayCC[5][2,]`, p = `r p_value(anovaConspicDisplayCC[6][2,])`; **Courtship displays**: Acromatic ($dl$); $F_{`r courship_anovaAC$NumDF[2]`,`r courship_anovaAC$DenDF[2]`}$ = `r courship_anovaAC[5][2,]`, p = `r p_value(courship_anovaAC[6][2,])`; Chromatic ($dS$): $F_{`r courship_anovaCC$NumDF[2]`,`r courship_anovaCC$DenDF[2]`}$ = `r courship_anovaCC[5][2,]`, p = `r p_value(courship_anovaCC[6][2,])`), and this was true across all body regions measured (See Supplemental Materials, Table S1).

>>>>

```{r getlibrary, echo = FALSE, results = "hide"}
# load libraries
devtools::install_github("karthik/wesanderson")
pacman::p_load(lme4, lmerTest, ggplot2, lsmeans, emmeans, multcomp, dplyr, wesanderson, patchwork, latex2exp, png, cowplot, magick, jpeg)

@@

# Center SVL to make intercept interpretable
Display_1$sc_SVL <- with(Display_1, scale(SVL, scale=FALSE))

@@

# Display dl
    ConspicDisplayAC <- lmer(dL ~ sc_SVL + Population + (1|ID), data=Display_1)
    summary(ConspicDisplayAC)
    anovaConspicDisplayAC <- anova(ConspicDisplayAC)

## Display dS
         ConspicDisplayCC <- lmer(dS ~ sc_SVL + Population + (1|ID), data=Display_1)
    anovaConspicDisplayCC <- anova(ConspicDisplayCC)

@@

# Load data
Courtship <- read.table("./data/Courtship_1.2.csv", 
                          header=TRUE, sep=",", dec=".", strip.white=TRUE)

# Center SVL do intercept is at the mean body size
Courtship$sc_SVL <- with(Courtship, scale(SVL, scale=FALSE))

# Courtship dl
ConspicCourtshipAC <- lmer(dL ~ sc_SVL + Population  + (1|ID), data=Courtship)
summary(ConspicCourtshipAC)
courship_anovaAC <- anova(ConspicCourtshipAC)

# Courtship dS
  ConspicCourtshipCC <- lmer(dS ~ sc_SVL + Population  + (1|ID), data=Courtship)
 courship_anovaCC <- anova(ConspicCourtshipCC)
```

@@

We manipulated both the social and predatory context chameleons encountered, in both their native Kenyan range and their introduced Hawaiian range, to test three hypotheses about colour signal evolution. First, we tested the hypothesis that relaxed predation pressure results in character release of a dynamic visual signal. Sexual selection favours more conspicious signals. As such, signals should evolve to be more conspicuous when predators are absent. In support of this prediction, male display colouration exhibited in social contexts (i.e., male-male contests and courtship) was more conspicuous to a conspecific in Hawaii compared with Kenya (**Male-Male Contests**: Acromatic contrast ($dl$); $F_{`r anovaConspicDisplayAC$NumDF[2]`,`r anovaConspicDisplayAC$DenDF[2]`}$ = `r anovaConspicDisplayAC[5][2,]`, p = `r p_value(anovaConspicDisplayAC[6][2,])`; Chromatic contrast ($dS$): $F_{`r anovaConspicDisplayCC$NumDF[2]`,`r anovaConspicDisplayCC$DenDF[2]`}$ = `r anovaConspicDisplayCC[5][2,]`, p = `r p_value(anovaConspicDisplayCC[6][2,])`; **Courtship displays**: Acromatic contrast ($dl$); $F_{`r courship_anovaAC$NumDF[2]`,`r courship_anovaAC$DenDF[2]`}$ = `r courship_anovaAC[5][2,]`, p = `r p_value(courship_anovaAC[6][2,])`; Chromatic contrast ($dS$): $F_{`r courship_anovaCC$NumDF[2]`,`r courship_anovaCC$DenDF[2]`}$ = `r courship_anovaCC[5][2,]`, p = `r p_value(courship_anovaCC[6][2,])`), and this was  true across all body regions measured (See Supplemental Materials, Table S1).

```{r Figure1}
## Make figures that average across body regions, but display Social Context

courtship_data <- Courtship %>% 
                  select(ID, Population, Colour, SVL, BodyRegion, Background, dS, dL)
  display_data <- Display_1 %>%
                  select(ID, Population, Colour, SVL, BodyRegion, Background, dS, dL)
combined_data <- rbind(courtship_data, display_data)

# Now calculate the averages for each population anc Colour (i.e., context)

summary_data <- combined_data %>%
                group_by(Population, Colour) %>%
                summarise( Mean_dS = mean(dS, na.rm = T), 
                             SE_dS = sd(dS)/sqrt(length(unique(ID))),
                             Upper_dS = Mean_dS + 1.96*SE_dS,
                             Lower_dS = Mean_dS - 1.96*SE_dS, 
                           Mean_dL = mean(dL, na.rm = T), 
                             SE_dL = sd(dL)/sqrt(length(unique(ID))),
                             Upper_dL = Mean_dL + 1.96*SE_dL,
                             Lower_dL = Mean_dL - 1.96*SE_dL) %>%
                mutate(Colour = if_else(Colour == "Courtship", "Courtship", "Male-male contest"))

males <- readPNG("./photos/male_fight.png", native = TRUE)
#males <- image_scale(males, "200x200")

females <- readPNG("./photos/courtship.png", native = TRUE)
#females <- image_scale(females, "200x200")

p1 <- ggplot(summary_data, aes(x = Population, y = Mean_dS, group = Colour, color = Colour)) +
    ylim(2.5, 6.5) + 
  geom_point(size = 3, position = position_dodge(width=0.5)) +
  geom_errorbar(aes(ymin = Lower_dS, ymax = Upper_dS), position = position_dodge(width=0.5), width = 0) + 
  geom_line(position = position_dodge(width=0.5)) + 
  scale_color_manual(values = wes_palette("Cavalcanti1")) + #Change color palette here see: https://github.com/karthik/wesanderson
  xlab("") + 
  ylab("Chromatic contrast (JND)") +
  annotate("segment", x = 0.85, xend = 1.85, y = 6.1, yend = 6.1, colour = "black") +
  annotate("segment", x = 1.12, xend = 2.12, y = 5.7, yend = 5.7, colour = "black") + 
  annotate("text", x = 0.85+(1.85-0.85)/2,  y = 6.2, label = "NS",  size = 6) + 
  annotate("text", x = 1.12+(2.12-1.12)/2, y = 5.8, label = "NS", size = 6) + 
  theme_bw() +
  labs(colour = "Social Context") +
  theme(legend.position = c(0.28, 0.08),
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text=element_text(size=18),
    axis.title=element_text(size=20,face="bold"),
    legend.text =element_text(size = 12),
    legend.title =element_text(size = 12, face = "bold")) +
   inset_element(males,
                left = 0.45,
                right = 0.90,
                bottom = 0.58,
                top = 0.75, ignore_tag = TRUE) + 
    inset_element(females,
                left = 0.30,
                right = 0.75,
                bottom = 0.15,
                top = 0.28, ignore_tag = TRUE) 
      #annotation_raster(males, xmin = 1.2, xmax = 1.9, ymin = 4.8, ymax = 5.3) + 
      #annotation_raster(females, xmin = 1, xmax = 1.7, ymin = 3.5, ymax = 4)

p2 <- ggplot(summary_data, aes(x = Population, y = Mean_dL, group = Colour, color = Colour)) +
  ylim(15, 45) + 
  geom_point(size = 3, position = position_dodge(width=0.5)) +
  geom_errorbar(aes(ymin = Lower_dL, ymax = Upper_dL), position = position_dodge(width=0.5), width = 0) + 
  geom_line(position = position_dodge(width=0.5)) + 
  scale_color_manual(values = wes_palette("Cavalcanti1")) + #Change color palette here see: https://github.com/karthik/wesanderson
  xlab("") + 
  ylab("Achromatic contrast (JND)") +
   annotate("segment", x = 0.90, xend = 1.90, y = 40, yend = 40, colour = "black") +
  annotate("segment", x = 1.12, xend = 2.12, y = 42, yend = 42, colour = "black") + 
  annotate("text", x = 0.9+((1.90 - 0.90)/2), y = 41, label = "**",  size = 6) + 
  annotate("text", x = 1.12+((2.12 - 1.12)/ 2), y = 43, label = "**", size = 6) + 
  theme_bw() +
  theme(legend.position = "none",
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text=element_text(size=18),
    axis.title=element_text(size=20,face="bold"),
    legend.text =element_text(size = 12),
    legend.title =element_text(size = 12, face = "bold")) +
    inset_element(males,
                left = 0.45,
                right = 0.90,
                bottom = 0.60,
                top = 0.75, ignore_tag = TRUE) + 
    inset_element(females,
                left = 0.05,
                right = 0.50,
                bottom = 0.25,
                top = 0.38, ignore_tag = TRUE)

plot_grid(p1, p2, labels = c("A", "B"), label_size = 16,
  label_fontface = "bold", rel_widths=c(1,1))

### 2021-04-22 supp.Rmd
Adding code now. Figure for social context done

```{r getlibrary, echo = FALSE, results = "hide"}
# load libraries
devtools::install_github("karthik/wesanderson")
pacman::p_load(lme4, lmerTest, ggplot2, lsmeans, emmeans, multcomp, dplyr, wesanderson, patchwork, pander, kableExtra, flextable)
```

@@

# Fit the model that esatimtes changes across body regions
ConspicDisplayAC <- lmer(dL ~ SVL + Population + BodyRegion + Background 
                         + Population:Background + Population:BodyRegion + (1|ID), data=Display_1)

@@

# Fit the model that esatimtes changes across body regions
  ConspicDisplayCC <- lmer(dS ~ SVL + Population + BodyRegion + Background 
                         + Population:Background + Population:BodyRegion + (1|ID), data=Display_1)
Display_1$PopBRInt <- interaction(Display_1$Population,Display_1$BodyRegion)

@@

# Courtship - Chromatic dl
ConspicCourtshipAC <- lmer(dL ~ SVL + Population + BodyRegion + Background 
                           + Population:Background + Population:BodyRegion + (1|ID), data=Courtship)

Courtship$PopBRInt <- interaction(Courtship$Population,Courtship$BodyRegion)
ConspicCourtshipAC2 <- lmer(dL ~ PopBRInt + (1|ID), data=Courtship)
summary(glht(ConspicCourtshipAC2, linfct = mcp(PopBRInt = c("Hawaii.gular - Kenya.gular = 0","Hawaii.midflank - Kenya.midflank = 0", "Hawaii.topflank - Kenya.topflank = 0", 
                                                            "Hawaii.tailbase - Kenya.tailbase = 0" ))))

ConspicCourtshipAC <- lmer(dL ~ SVL + Population + BodyRegion +  
                             + Population:BodyRegion + (1|ID), data=Courtship)
anova(ConspicCourtshipAC)
ranova(ConspicCourtshipAC)

# Courtship - Chromatic dS
ConspicCourtshipCC <- lmer(dS ~ SVL + Population + BodyRegion + Background 
                           + Population:Background + Population:BodyRegion + (1|ID), data=Courtship)
Courtship$PopBRInt <- interaction(Courtship$Population,Courtship$BodyRegion)
ConspicCourtshipCC2 <- lmer(dS ~ PopBRInt + (1|ID), data=Courtship)
summary(glht(ConspicCourtshipCC2, linfct = mcp(PopBRInt = c("Hawaii.gular - Kenya.gular = 0","Hawaii.midflank - Kenya.midflank = 0", "Hawaii.topflank - Kenya.topflank = 0", 
                                                            "Hawaii.tailbase - Kenya.tailbase = 0" ))))

@@

```{FigS1, fig.width = 5, fig.height = 10, fig.caption = "test"}

#Making a point plot with error bars split by body size and population 
#Compute raw means and standard errors for body part and population for dS and assigned this data into Display_plot_dS_dat
Display_plot_dS_dat <- Display_1 %>% #data for dS Chromatic constrast
  group_by(Population, BodyRegion) %>% 
  summarise(Mean = mean(dS, na.rm = T), 
            SE = sd(dS)/sqrt(length(unique(ID))),
            Upper = Mean + 1.96*SE,
            Lower = Mean - 1.96*SE)

@@

#Plotting Chromatic contrast (dS)
p1 <- ggplot(Display_plot_dS_dat, aes(x = Population, y = Mean, group = BodyRegion, color = BodyRegion)) +
  geom_point(size = 3) +
  geom_line() +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0) + 
  scale_color_manual(values = wes_palette("Cavalcanti1")) + #Change color palette here see: https://github.com/karthik/wesanderson
  xlab("") + 
  ylab(TeX("Chromatic contrast (JND)")) +
  theme_bw() +
  theme(legend.position = "none",
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text=element_text(size=18),
    axis.title=element_text(size=20,face="bold"),
    legend.text =element_text(size = 12),
    legend.title =element_text(size = 12, face = "bold"))

#Plotting Achromatic contrast (dL)
p2 <- ggplot(Display_plot_dL_dat, aes(x = Population, y = Mean, group = BodyRegion, color = BodyRegion)) +
  geom_point(size = 3) +
  geom_line() +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0) + 
  scale_color_manual(values = wes_palette("Cavalcanti1")) + #Change color palette here see: https://github.com/karthik/wesanderson
  xlab("") + 
  ylab(TeX("Achromatic contrast (JND)")) +
  theme_bw() +
  theme(#legend.position = "none",
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text=element_text(size=18),
    axis.title=element_text(size=20,face="bold"),
    legend.text =element_text(size = 12),
    legend.title =element_text(size = 12, face = "bold"))

@@

#Plotting Chromatic contrast (dS)
p3 <- ggplot(Courtship_plot_dS_dat, aes(x = Population, y = Mean, group = BodyRegion, color = BodyRegion)) +
  geom_point(size = 3) +
  geom_line() +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0) + 
  scale_color_manual(values = wes_palette("Cavalcanti1")) + #Change color palette here see: https://github.com/karthik/wesanderson
  xlab("") + 
  ylab(TeX("Chromatic contrast (JND)")) +
  theme_bw() +
  theme(legend.position = "none",
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text=element_text(size=18),
    axis.title=element_text(size=20,face="bold"),
    legend.text =element_text(size = 12),
    legend.title =element_text(size = 12, face = "bold"))

#Plotting Achromatic contrast (dL)
p4 <- ggplot(Courtship_plot_dL_dat, aes(x = Population, y = Mean, group = BodyRegion, color = BodyRegion)) +
  geom_point(size = 3) +
  geom_line() +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0) + 
  scale_color_manual(values = wes_palette("Cavalcanti1")) + #Change color palette here see: https://github.com/karthik/wesanderson
  xlab("") + 
  ylab(TeX("Achromatic contrast (JND)")) +
  theme_bw() +
  theme(legend.position = "none",
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text=element_text(size=18),
    axis.title=element_text(size=20,face="bold"),
    legend.text =element_text(size = 12),
    legend.title =element_text(size = 12, face = "bold"))

@@

# References

>>>>

```{r getlibrary, echo = FALSE, results = "hide"}
# load libraries
devtools::install_github("karthik/wesanderson")
pacman::p_load(lme4, lmerTest, ggplot2, lsmeans, emmeans, multcomp, dplyr, wesanderson, patchwork, pander, kableExtra, flextable, jpeg)
```

@@

# Center SVL to make intercept interpretable
Display_1$sc_SVL <- with(Display_1, scale(SVL, scale=FALSE))

# Fit the model that esatimtes changes across body regions
ConspicDisplayAC <- lmer(dL ~ sc_SVL + Population + BodyRegion + Background 
                         + Population:Background + Population:BodyRegion + (1|ID), data=Display_1)

@@

# Fit the model that esatimtes changes across body regions
  ConspicDisplayCC <- lmer(dS ~ sc_SVL + Population + BodyRegion + Background 
                         + Population:Background + Population:BodyRegion + (1|ID), data=Display_1)
Display_1$PopBRInt <- interaction(Display_1$Population,Display_1$BodyRegion)

@@

# Center SVL to make intercept interpretable
Courtship$sc_SVL <- with(Courtship, scale(SVL, scale=FALSE))

# Fit model
ConspicCourtshipAC <- lmer(dL ~ sc_SVL + Population + BodyRegion +  
                             + Population:BodyRegion + (1|ID), data=Courtship)
anova(ConspicCourtshipAC)

ConspicCourtshipAC <- lmer(dL ~ sc_SVL + Population + BodyRegion + (1|ID), data=Courtship)
summary(ConspicCourtshipAC)
anova(ConspicCourtshipAC)

# Courtship - Chromatic dl

Courtship$PopBRInt <- interaction(Courtship$Population,Courtship$BodyRegion)
ConspicCourtshipAC2 <- lmer(dL ~ PopBRInt + (1|ID), data=Courtship)
summary(glht(ConspicCourtshipAC2, linfct = mcp(PopBRInt = c("Hawaii.gular - Kenya.gular = 0",
                                                            "Hawaii.midflank - Kenya.midflank = 0", 
                                                            "Hawaii.topflank - Kenya.topflank = 0", 
                                                            "Hawaii.tailbase - Kenya.tailbase = 0" ))))

# Courtship - Chromatic dS
ConspicCourtshipCC <- lmer(dS ~ SVL + Population + BodyRegion + Background 
                           + Population:Background + Population:BodyRegion + (1|ID), data=Courtship)
Courtship$PopBRInt <- interaction(Courtship$Population,Courtship$BodyRegion)
ConspicCourtshipCC2 <- lmer(dS ~ PopBRInt + (1|ID), data=Courtship)
summary(glht(ConspicCourtshipCC2, linfct = mcp(PopBRInt = c("Hawaii.gular - Kenya.gular = 0",
                                                            "Hawaii.midflank - Kenya.midflank = 0", 
                                                            "Hawaii.topflank - Kenya.topflank = 0", 
                                                            "Hawaii.tailbase - Kenya.tailbase = 0" ))))

@@

```{r FigS1, fig.width = 14.33333, fig.height = 11.00000, fig.cap = "Chormatic (A, C) and Achromatic (B, D) contrast in just noticible differences (JND) for Hawaiian and Kenyan lizards relative to their environments. All four body regions (gular, mid-flank, tailbase and topflank) are shown averaged across stems and leaves found in their habitat. Mean JNDs are provided along with 95% confidence intervals. A & B represent male-male contest displays whereas C & D represent courtship displays"}

#Making a point plot with error bars split by body size and population 
#Compute raw means and standard errors for body part and population for dS and assigned this data into Display_plot_dS_dat
Display_plot_dS_dat <- Display_1 %>% #data for dS Chromatic constrast
  group_by(Population, BodyRegion) %>% 
  summarise( Mean = mean(dS, na.rm = T), 
               SE = sd(dS)/sqrt(length(unique(ID))),
            Upper = Mean + 1.96*SE,
            Lower = Mean - 1.96*SE)

@@

#Plotting Chromatic contrast (dS)
p1 <- ggplot(Display_plot_dS_dat, aes(x = Population, y = Mean, group = BodyRegion, color = BodyRegion)) +
  geom_point(size = 3, position = position_dodge(width=0.2)) +
  geom_line(position = position_dodge(width=0.2)) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = position_dodge(width=0.2), width = 0) + 
  scale_color_manual(values = wes_palette("Cavalcanti1")) + #Change color palette here see: https://github.com/karthik/wesanderson
  xlab("") + 
  ylab("Chromatic contrast (JND)") +
  theme_bw() +
  theme(legend.position = "none",
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text=element_text(size=18),
    axis.title=element_text(size=20,face="bold"),
    legend.text =element_text(size = 12),
    legend.title =element_text(size = 12, face = "bold"))

#Plotting Achromatic contrast (dL)
p2 <- ggplot(Display_plot_dL_dat, aes(x = Population, y = Mean, group = BodyRegion, color = BodyRegion)) +
  geom_point(size = 3, position = position_dodge(width=0.2)) +
  geom_line(position = position_dodge(width=0.2)) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = position_dodge(width=0.2), width = 0) + 
  scale_color_manual(values = wes_palette("Cavalcanti1")) + #Change color palette here see: https://github.com/karthik/wesanderson
  xlab("") + 
  ylab("Achromatic contrast (JND)") +
  theme_bw() +
  labs(color = "Body Region") + 
  theme(#legend.position = "none",
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text=element_text(size=18),
    axis.title=element_text(size=20,face="bold"),
    legend.text =element_text(size = 12),
    legend.title =element_text(size = 12, face = "bold"))

@@

#Plotting Chromatic contrast (dS)
p3 <- ggplot(Courtship_plot_dS_dat, aes(x = Population, y = Mean, group = BodyRegion, color = BodyRegion)) +
  geom_point(size = 3, position = position_dodge(width=0.2)) +
  geom_line(position = position_dodge(width=0.2)) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = position_dodge(width=0.2), width = 0) + 
  scale_color_manual(values = wes_palette("Cavalcanti1")) + #Change color palette here see: https://github.com/karthik/wesanderson
  xlab("") + 
  ylab("Chromatic contrast (JND)") +
  theme_bw() +
  theme(legend.position = "none",
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text=element_text(size=18),
    axis.title=element_text(size=20,face="bold"),
    legend.text =element_text(size = 12),
    legend.title =element_text(size = 12, face = "bold"))

#Plotting Achromatic contrast (dL)
p4 <- ggplot(Courtship_plot_dL_dat, aes(x = Population, y = Mean, group = BodyRegion, color = BodyRegion)) +
  geom_point(size = 3, position = position_dodge(width=0.2)) +
  geom_line(position = position_dodge(width=0.2)) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = position_dodge(width=0.2), width = 0) + 
  scale_color_manual(values = wes_palette("Cavalcanti1")) + #Change color palette here see: https://github.com/karthik/wesanderson
  xlab("") + 
  ylab("Achromatic contrast (JND)") +
  theme_bw() +
  theme(legend.position = "none",
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text=element_text(size=18),
    axis.title=element_text(size=20,face="bold"),
    legend.text =element_text(size = 12),
    legend.title =element_text(size = 12, face = "bold"))

@@

```{r FigS2}

files <- list.files("./photos/ESM/")
img1 <- readJPEG(paste0("./photos/ESM/", files[1]))
img2 <- readJPEG(paste0("./photos/ESM/", files[2]))
img3 <- readJPEG(paste0("./photos/ESM/", files[3]))
img4 <- readJPEG(paste0("./photos/ESM/", files[4]))
img5 <- readJPEG(paste0("./photos/ESM/", files[5]))
img6 <- readJPEG(paste0("./photos/ESM/", files[6]))

p1 <- cowplot::ggdraw()+
        cowplot::draw_image(img1)
p2 <- cowplot::ggdraw()+
        cowplot::draw_image(img2)
p3 <- cowplot::ggdraw()+
        cowplot::draw_image(img3)
p4 <- cowplot::ggdraw()+
        cowplot::draw_image(img4)
p5 <- cowplot::ggdraw()+
        cowplot::draw_image(img5)
p6 <- cowplot::ggdraw()+
        cowplot::draw_image(img6)

(p1 + p3 + p6) / (p2 + p5 + p4) + plot_annotation(tag_levels = c("A", "B", "C", "D", "E", "F"))

```
# References
